Graph Topology Learning from Binary Signals on Graph

### 2022-04-27 poster html copy/poster html.Rmd
poster update

---
title: Graph Topology Learning from Binary Signals on Graph
author:
  - name: Skip Moses
  - name: Jing Guo
affiliation:
    address: Department of Mathematics and Statistics, California State University, Chico
column_numbers: 4
primary_colour: "#9D2235"
secondary_colour: "#FFFFFF"
poster_height: "36in"
poster_width: "60in"
# logoright_name: 
# logoleft_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
output: 
  posterdown::posterdown_html:
    self_contained: false
bibliography: ref.bib
---

>>>>

---
title: Graph Topology Learning from Binary Signals on Graph
author:
  - name: Skip Moses
  - name: Jing Guo
affiliation:
    address: Department of Mathematics and Statistics, California State University, Chico
column_numbers: 4
primary_colour: "#9D2235"
secondary_colour: "#FFFFFF"
poster_height: "36in"
poster_width: "60in"
logoright_name: Chico-State-Flame-Cardinal300dpi.png
# logoleft_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
output: 
  posterdown::posterdown_html:
    self_contained: false
bibliography: ref.bib
---
